\begin{abstract}


A software defined network (SDN) enables  
many techniques (e.g., artificial intelligence, or AI) to be implemented easily, and in
turn these techniques greatly improve the performance and resilience of the SDN system.
Unfortunately, all the existing SDN systems in wireless sensor networks
are implemented in simulators, and there is no practical 
SDN implementation for wireless sensor networks.


In this paper, we present {\sdn}, the first practical SDN wireless sensor network system,
which achieves intelligence, high-performance and resilience simultaneously.
In {\sdn}, we utilize a set of unmanned aerial vehicles (UAVs) to serve as the SDN controllers. 
Sensor nodes communicate with UAVs when they are within one-hop communication ranges, 
greatly improving throughputs and reducing the sensor nodes' energy consumption. 
{\sdn} includes easy-to-use SDN interfaces and we have implemented five SDN applications, namely
routing, multi-task, network diagnosis, AI energy exhaustion prediction, and AI node selection.
{\sdn} is a ecosystem where all SDN applications run simultaneously to benefit each other.
Our evaluation shows that {\sdn}'s throughput is  {\simpleTput} higher than two 
notable traditional sensor network routing protocols.
%by using the basic {\sdn} routing algorithm. 
Meanwhile, the average lifetime of sensor nodes in {\sdn} is 
{\simpleLife} longer than these two protocols. 
%By running our AI energy prediction %and AI selection 
%application,  the nodes' lifetime in {\sdn} further improves  by {\totalLife}. %and {\seleLife}
All source code and results of {\sdn} are released on \emph{anonymous}.
%


%throughput improves by 1.2X compared to two notable traditional sensor network routing protocols.

%throughput    comparing with other provence,  still maintains initial throughput 
%when  


%!TEX encoding = UTF-8 Unicodestate-of-the-art

\end{abstract}
